---
output: github_document
date: "2026-09-17"
---

# DOT syntax options and translators

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


> **Edge options**
> [dir = ...]
> forward (default), both, back, none (undirected edge)
> [arrowhead / arrowtail = ...]
> normal, inv, dot, odot, invdot, invodot, none, tee, empty, invempty, diamond, odiamond, ediamond, crow, box, obox, open, halfopen, vee
> [color = ...]


There are a range of ways that graphical causal models are represented, beyond blobs and arrows. Here we attempt to document the various options, provide a way to represent this in the DOT language, and provide functions to read this into `DAGitty` or `tidygraph` objects. 

To cover:

- Double headed arrows as unmeasured confounders
- Partial ancestral graphs (PAGs). These include `@->`, `<->` and `@-@`. Will need a way to visually distinguish the last two. 
- Generally adding flavour to any edge - such as using dashed lines to indicate uncertainty about an edge. 

```{r pag-example}
digraph pag_example {
  edge [dir = both, arrowtail = none, arrowhead = normal]  /* default: tail -> arrowhead */

  A -> B [arrowtail = odot,  arrowhead = normal]  /* A o-> B  */
  B -> C [arrowtail = normal, arrowhead = normal] /* B <-> C  */
  A -> D [arrowtail = odot,  arrowhead = odot]    /* A o-o D  */
}
```
